Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach

### 2022-09-25 docs/attachment-bayes-factor.tex
update bookdown

\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach},
  pdfauthor={Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs

@@

\usepackage{titlepic}
\titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}

\title{Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2021-11-28}

@@

@@

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version {[}ECR-RC, \citet{Brenning2014ThePQ}; marciBriefExperiencesClose2019{]} completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of \emph{anxiety} and \emph{avoidance}:

@@

In Figure\textasciitilde\ref{fig:plot-scores-mother}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to mother attachment styles. The frequencies of mother attachment styles according to gender are reported in Table\textasciitilde{}\ref{tab:table-cluster-mother}.

@@

\begin{verbatim}
##   # Best model-based clustering for mother attachment
## Best BIC values:
##              EEV,6       EEV,7      EEV,8
## BIC      -23978.93 -24842.2437 -25039.952
## BIC diff      0.00   -863.3168  -1061.025
\end{verbatim}

@@

In Figure\textasciitilde\ref{fig:plot-scores-father}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to father attachment styles. The frequencies of father attachment styles according to gender are reported in Table\textasciitilde{}\ref{tab:table-cluster-father}.

@@

\begin{verbatim}
##   # Best model-based clustering for father attachment
## Best BIC values:
##              EEV,9       EEV,8      EEV,5
## BIC      -25351.43 -25790.9130 -25905.197
## BIC diff      0.00   -439.4807   -553.765
\end{verbatim}

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table\textasciitilde{}\ref(tab:table-cluster-ext).

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1720}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0089}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2300}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4180}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_zinb)}
\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may be}
\DocumentationTok{\#\#   unreliable.}
\DocumentationTok{\#\# \# R2 for Mixed Models}
\DocumentationTok{\#\# }
\DocumentationTok{\#\#   Conditional R2: 0.191}
\DocumentationTok{\#\#      Marginal R2: 0.091}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0859}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0247}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0003}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0898}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_mother)}
\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may be}
\DocumentationTok{\#\#   unreliable.}
\DocumentationTok{\#\# \# R2 for Mixed Models}
\DocumentationTok{\#\# }
\DocumentationTok{\#\#   Conditional R2: 0.168}
\DocumentationTok{\#\#      Marginal R2: 0.071}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
##                   prior     class                          coef    group resp dpar nlpar bound       source
##            normal(0, 3)         b                                                                      user
##            normal(0, 3)         b                 fatherAnxious                                (vectorized)
##            normal(0, 3)         b                fatherAvoidant                                (vectorized)
##            normal(0, 3)         b                 fatherFearful                                (vectorized)
##            normal(0, 3)         b                       genderM                                (vectorized)
##            normal(0, 3)         b                 motherAnxious                                (vectorized)
##            normal(0, 3)         b   motherAnxious:fatherAnxious                                (vectorized)
##            normal(0, 3)         b  motherAnxious:fatherAvoidant                                (vectorized)
##            normal(0, 3)         b   motherAnxious:fatherFearful                                (vectorized)
##            normal(0, 3)         b                motherAvoidant                                (vectorized)
##            normal(0, 3)         b  motherAvoidant:fatherAnxious                                (vectorized)
##            normal(0, 3)         b motherAvoidant:fatherAvoidant                                (vectorized)
##            normal(0, 3)         b  motherAvoidant:fatherFearful                                (vectorized)
##            normal(0, 3)         b                 motherFearful                                (vectorized)
##            normal(0, 3)         b   motherFearful:fatherAnxious                                (vectorized)
##            normal(0, 3)         b  motherFearful:fatherAvoidant                                (vectorized)
##            normal(0, 3)         b   motherFearful:fatherFearful                                (vectorized)
##            normal(0, 3)         b                                               zi             (vectorized)
##            normal(0, 3)         b                       genderM                 zi             (vectorized)
##  student_t(3, 0.7, 2.5) Intercept                                                                   default
##          logistic(0, 1) Intercept                                               zi                  default
##    student_t(3, 0, 2.5)        sd                                                                   default
##    student_t(3, 0, 2.5)        sd                                               zi                  default
##    student_t(3, 0, 2.5)        sd                               ID_class                       (vectorized)
##    student_t(3, 0, 2.5)        sd                     Intercept ID_class                       (vectorized)
##    student_t(3, 0, 2.5)        sd                               ID_class        zi             (vectorized)
##    student_t(3, 0, 2.5)        sd                     Intercept ID_class        zi             (vectorized)
##       gamma(0.01, 0.01)     shape                                                                   default
\end{verbatim}

@@

\begin{verbatim}
##  Family: zero_inflated_negbinomial 
##   Links: mu = log; shape = identity; zi = logit 
## Formula: externalizing_sum ~ gender + mother * father + (1 | ID_class) 
##          zi ~ gender + (1 | ID_class)
##    Data: data (Number of observations: 847) 
## Samples: 6 chains, each with iter = 10000; warmup = 2000; thin = 1;
##          total post-warmup samples = 48000
## 
## Group-Level Effects: 
## ~ID_class (Number of levels: 50) 
##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
## sd(Intercept)        0.30      0.07     0.17     0.45 1.00    14161    20827
## sd(zi_Intercept)     1.14      0.29     0.68     1.82 1.00    22361    31673
## 
## Population-Level Effects: 
##                               Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
## Intercept                         0.98      0.13     0.72     1.24 1.00    35521    38291
## zi_Intercept                     -1.33      0.33    -2.09    -0.78 1.00    36797    30278
## genderM                           0.32      0.08     0.16     0.49 1.00    81905    36734
## motherAnxious                     0.32      0.19    -0.05     0.70 1.00    39619    37732
## motherAvoidant                    0.17      0.26    -0.33     0.69 1.00    37098    36353
## motherFearful                     0.69      0.41    -0.07     1.54 1.00    34182    30539
## fatherAnxious                     0.22      0.20    -0.16     0.60 1.00    40404    38489
## fatherAvoidant                   -0.45      0.22    -0.87    -0.02 1.00    40412    38016
## fatherFearful                     0.11      0.42    -0.69     0.96 1.00    35432    34390
## motherAnxious:fatherAnxious      -0.39      0.28    -0.94     0.15 1.00    36701    36495
## motherAvoidant:fatherAnxious     -0.12      0.34    -0.80     0.53 1.00    36329    36398
## motherFearful:fatherAnxious      -0.43      0.51    -1.46     0.55 1.00    35084    32876
## motherAnxious:fatherAvoidant      0.33      0.29    -0.25     0.89 1.00    36157    37830
## motherAvoidant:fatherAvoidant     0.61      0.34    -0.06     1.26 1.00    34169    35603
## motherFearful:fatherAvoidant      0.30      0.48    -0.68     1.20 1.00    32533    31702
## motherAnxious:fatherFearful      -0.06      0.48    -1.02     0.86 1.00    34008    34560
## motherAvoidant:fatherFearful      0.09      0.57    -1.04     1.19 1.00    34795    33933
## motherFearful:fatherFearful      -0.26      0.60    -1.48     0.86 1.00    30725    30729
## zi_genderM                       -0.78      0.29    -1.38    -0.23 1.00    70555    35796
## 
## Family Specific Parameters: 
##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
## shape     1.63      0.24     1.22     2.14 1.00    34643    32767
## 
## Samples were drawn using sampling(NUTS). For each parameter, Bulk_ESS
## and Tail_ESS are effective sample size measures, and Rhat is the potential
## scale reduction factor on split chains (at convergence, Rhat = 1).
\end{verbatim}

@@

\caption{\label{tab:table-bf-results-ext}Bayes factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).}
\centering
\begin{tabular}[t]{rcc>{\centering\arraybackslash}m{1cm}}
\toprule
\textbf{Hypothesis} & \textbf{Bayes Factor} & \textbf{Posterior Probability} & \textbf{ }\\
\midrule
Null & 2.9e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_null.png}\\
Monotropy & 2.6e+13 & 0.98 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_monotropy.png}\\
Hierarchy & 2.7e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_hierarchy.png}\\
Independence & 3.9e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_independence.png}\\
Integration & 3.2e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_integration.png}\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:table-sens-prior-analysis-ext}Bayes factor encompassing model and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}rcccrcccrcc}
\toprule
\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, .5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 1)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 3)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 10)$}} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
\textbf{Hypothesis} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP}\\
\midrule
\textbf{Null} & 8.2e+01 & 0.00 & 9.4e+04 & 0.00 & 2.9e+11 & 0.01 & 4.7e+14 & 0.03 & 1.5e+19 & 0.11\\
\textbf{Monotropy} & 1.2e+05 & 0.67 & 6.3e+07 & 0.90 & 2.6e+13 & 0.98 & 1.6e+16 & 0.97 & 1.2e+20 & 0.89\\
\textbf{Hierarchy} & 4.9e+04 & 0.28 & 6.1e+06 & 0.09 & 2.7e+11 & 0.01 & 6.7e+13 & 0.00 & 1.2e+17 & 0.00\\
\textbf{Independence} & 4.4e+03 & 0.02 & 2.6e+05 & 0.00 & 3.9e+09 & 0.00 & 5.8e+11 & 0.00 & 5.1e+14 & 0.00\\
\textbf{Integration} & 4.6e+03 & 0.03 & 3.3e+05 & 0.00 & 3.2e+09 & 0.00 & 3.3e+11 & 0.00 & 1.5e+14 & 0.00\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{r2\_ext}
\DocumentationTok{\#\#     Estimate  Est.Error       Q2.5     Q97.5}
\DocumentationTok{\#\# R2 0.1482686 0.02972484 0.09435914 0.2106949}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{r2\_int}
\DocumentationTok{\#\#     Estimate  Est.Error      Q2.5    Q97.5}
\DocumentationTok{\#\# R2 0.2224337 0.02977471 0.1651088 0.281678}
\end{Highlighting}
\end{Shaded}

>>>>

\usepackage{iftex}
\ifPDFTeX

@@

@@

\usepackage{titlepic}
\titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach},
  pdfauthor={Claudio Zandonella Callegher, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Evaluating Informative Hypotheses with Equality and Inequality Constraints: A Tutorial Using the Bayes Factor via the Encompassing Prior Approach}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Supplemental Material}
\author{\href{https://claudiozandonella.netlify.app/}{Claudio Zandonella Callegher}, Tatiana Marci, Pietro De Carli, and Gianmarco Altoè}
\date{2022-09-25}

@@

\begin{verbatim}
## Tartgets loaded!
\end{verbatim}

@@

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version \citep[ECR-RC,][]{Brenning2014ThePQ, marciBriefExperiencesClose2019} completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of \emph{anxiety} and \emph{avoidance}:

@@

In Figure\textasciitilde\ref{fig:plot-scores-mother}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to mother attachment styles. The frequencies of mother attachment styles according to gender are reported in Table\textasciitilde\ref{tab:table-cluster-mother}.

@@

\begin{verbatim}
##   # Best model-based clustering for mother attachment
## Best BIC values:
##              EEV,6       EEV,7       EEV,9
## BIC      -23978.93 -24842.2954 -24969.9125
## BIC diff      0.00   -863.3681   -990.9852
\end{verbatim}

@@

In Figure\textasciitilde\ref{fig:plot-scores-father}, Anxiety (``\emph{Anx}'') and Avoidance (``\emph{Av}'') scores are presented according to father attachment styles. The frequencies of father attachment styles according to gender are reported in Table\textasciitilde\ref{tab:table-cluster-father}.

@@

\begin{verbatim}
##   # Best model-based clustering for father attachment
## Best BIC values:
##              EEV,9       EEV,5       EEV,8
## BIC      -25351.48 -25905.1973 -25979.1378
## BIC diff      0.00   -553.7208   -627.6613
\end{verbatim}

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table\textasciitilde\ref{tab:table-cluster-int}.

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_zinb, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\# }\AlertTok{NOTE}\DocumentationTok{: Results may be misleading due to involvement in interactions}
\DocumentationTok{\#\#  contrast           estimate    SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2856 0.140 825  {-}2.034  0.1719}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.162 825  {-}1.902  0.2228}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5617 0.178 825  {-}3.149  0.0089}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0224 0.124 825  {-}0.181  0.9978}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2761 0.146 825  {-}1.885  0.2300}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2537 0.167 825  {-}1.522  0.4179}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender, father }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_zinb)}
\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may}
\DocumentationTok{\#\#   be unreliable.}
\DocumentationTok{\#\# \# R2 for Mixed Models}
\DocumentationTok{\#\# }
\DocumentationTok{\#\#   Conditional R2: 0.191}
\DocumentationTok{\#\#      Marginal R2: 0.091}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{emmeans}\SpecialCharTok{::}\FunctionTok{contrast}\NormalTok{(emmeans}\SpecialCharTok{::}\FunctionTok{emmeans}\NormalTok{(fit\_ext\_mother, }\AttributeTok{specs =} \SpecialCharTok{\textasciitilde{}}\NormalTok{ mother ),}
                  \StringTok{"pairwise"}\NormalTok{, }\AttributeTok{adjust =} \StringTok{"mvt"}\NormalTok{)}
\DocumentationTok{\#\#  contrast           estimate     SE  df t.ratio p.value}
\DocumentationTok{\#\#  Secure {-} Anxious    {-}0.2432 0.1034 837  {-}2.353  0.0859}
\DocumentationTok{\#\#  Secure {-} Avoidant   {-}0.3080 0.1091 837  {-}2.823  0.0243}
\DocumentationTok{\#\#  Secure {-} Fearful    {-}0.5268 0.1313 837  {-}4.011  0.0004}
\DocumentationTok{\#\#  Anxious {-} Avoidant  {-}0.0648 0.0981 837  {-}0.661  0.9107}
\DocumentationTok{\#\#  Anxious {-} Fearful   {-}0.2836 0.1216 837  {-}2.333  0.0903}
\DocumentationTok{\#\#  Avoidant {-} Fearful  {-}0.2188 0.1276 837  {-}1.714  0.3135}
\DocumentationTok{\#\# }
\DocumentationTok{\#\# Results are averaged over the levels of: gender }
\DocumentationTok{\#\# Results are given on the log (not the response) scale. }
\DocumentationTok{\#\# P value adjustment: mvt method for 6 tests}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{performance}\SpecialCharTok{::}\FunctionTok{r2}\NormalTok{(fit\_ext\_mother)}
\DocumentationTok{\#\# Warning: mu of 4.2 is too close to zero, estimate of random effect variances may}
\DocumentationTok{\#\#   be unreliable.}
\DocumentationTok{\#\# \# R2 for Mixed Models}
\DocumentationTok{\#\# }
\DocumentationTok{\#\#   Conditional R2: 0.168}
\DocumentationTok{\#\#      Marginal R2: 0.071}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
##                   prior     class                          coef    group resp dpar nlpar lb ub       source
##            normal(0, 3)         b                                                                      user
##            normal(0, 3)         b                 fatherAnxious                                (vectorized)
##            normal(0, 3)         b                fatherAvoidant                                (vectorized)
##            normal(0, 3)         b                 fatherFearful                                (vectorized)
##            normal(0, 3)         b                       genderM                                (vectorized)
##            normal(0, 3)         b                 motherAnxious                                (vectorized)
##            normal(0, 3)         b   motherAnxious:fatherAnxious                                (vectorized)
##            normal(0, 3)         b  motherAnxious:fatherAvoidant                                (vectorized)
##            normal(0, 3)         b   motherAnxious:fatherFearful                                (vectorized)
##            normal(0, 3)         b                motherAvoidant                                (vectorized)
##            normal(0, 3)         b  motherAvoidant:fatherAnxious                                (vectorized)
##            normal(0, 3)         b motherAvoidant:fatherAvoidant                                (vectorized)
##            normal(0, 3)         b  motherAvoidant:fatherFearful                                (vectorized)
##            normal(0, 3)         b                 motherFearful                                (vectorized)
##            normal(0, 3)         b   motherFearful:fatherAnxious                                (vectorized)
##            normal(0, 3)         b  motherFearful:fatherAvoidant                                (vectorized)
##            normal(0, 3)         b   motherFearful:fatherFearful                                (vectorized)
##                  (flat)         b                                               zi                  default
##                  (flat)         b                       genderM                 zi             (vectorized)
##  student_t(3, 0.7, 2.5) Intercept                                                                   default
##          logistic(0, 1) Intercept                                               zi                  default
##    student_t(3, 0, 2.5)        sd                                                         0         default
##    student_t(3, 0, 2.5)        sd                                               zi        0         default
##    student_t(3, 0, 2.5)        sd                               ID_class                  0    (vectorized)
##    student_t(3, 0, 2.5)        sd                     Intercept ID_class                  0    (vectorized)
##    student_t(3, 0, 2.5)        sd                               ID_class        zi        0    (vectorized)
##    student_t(3, 0, 2.5)        sd                     Intercept ID_class        zi        0    (vectorized)
##       gamma(0.01, 0.01)     shape                                                         0         default
\end{verbatim}

@@

\begin{verbatim}
##  Family: zero_inflated_negbinomial 
##   Links: mu = log; shape = identity; zi = logit 
## Formula: externalizing_sum ~ gender + mother * father + (1 | ID_class) 
##          zi ~ gender + (1 | ID_class)
##    Data: data (Number of observations: 847) 
##   Draws: 6 chains, each with iter = 10000; warmup = 2000; thin = 1;
##          total post-warmup draws = 48000
## 
## Group-Level Effects: 
## ~ID_class (Number of levels: 50) 
##                  Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
## sd(Intercept)        0.30      0.07     0.17     0.45 1.00    14452    20584
## sd(zi_Intercept)     1.14      0.29     0.68     1.82 1.00    21599    30432
## 
## Population-Level Effects: 
##                               Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
## Intercept                         0.98      0.13     0.72     1.24 1.00    36946    39083
## zi_Intercept                     -1.33      0.33    -2.08    -0.79 1.00    37409    31478
## genderM                           0.32      0.08     0.16     0.49 1.00    83483    38460
## motherAnxious                     0.32      0.19    -0.06     0.69 1.00    40607    39458
## motherAvoidant                    0.17      0.26    -0.33     0.69 1.00    39406    36276
## motherFearful                     0.69      0.41    -0.07     1.53 1.00    35752    33258
## fatherAnxious                     0.22      0.19    -0.16     0.60 1.00    41153    37645
## fatherAvoidant                   -0.45      0.21    -0.87    -0.03 1.00    43962    38015
## fatherFearful                     0.11      0.42    -0.68     0.97 1.00    33620    33965
## motherAnxious:fatherAnxious      -0.39      0.28    -0.93     0.15 1.00    37290    38104
## motherAvoidant:fatherAnxious     -0.12      0.34    -0.79     0.53 1.00    37877    36168
## motherFearful:fatherAnxious      -0.43      0.51    -1.45     0.55 1.00    36742    34591
## motherAnxious:fatherAvoidant      0.33      0.29    -0.24     0.89 1.00    38934    38185
## motherAvoidant:fatherAvoidant     0.60      0.33    -0.05     1.25 1.00    37462    34839
## motherFearful:fatherAvoidant      0.30      0.48    -0.67     1.20 1.00    34490    33126
## motherAnxious:fatherFearful      -0.06      0.48    -1.03     0.87 1.00    33089    34838
## motherAvoidant:fatherFearful      0.09      0.57    -1.04     1.19 1.00    35141    36840
## motherFearful:fatherFearful      -0.27      0.59    -1.46     0.86 1.00    29919    31952
## zi_genderM                       -0.78      0.29    -1.38    -0.24 1.00    68477    37227
## 
## Family Specific Parameters: 
##       Estimate Est.Error l-95% CI u-95% CI Rhat Bulk_ESS Tail_ESS
## shape     1.64      0.24     1.22     2.14 1.00    34980    35143
## 
## Draws were sampled using sampling(NUTS). For each parameter, Bulk_ESS
## and Tail_ESS are effective sample size measures, and Rhat is the potential
## scale reduction factor on split chains (at convergence, Rhat = 1).
\end{verbatim}

@@

\caption{\label{tab:table-bf-results-ext}Bayes factor encompassing model and hypothesis posterior probabilities  ($n_{subj} = 847$).}
\centering
\begin{tabular}[t]{rcc>{\centering\arraybackslash}m{1cm}}
\toprule
\textbf{Hypothesis} & \textbf{Bayes Factor} & \textbf{Posterior Probability} & \textbf{ }\\
\midrule
Null & 2.4e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_null.png}\\
Monotropy & 2.5e+13 & 0.98 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_monotropy.png}\\
Hierarchy & 2.9e+11 & 0.01 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_hierarchy.png}\\
Independence & 4.0e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_independence.png}\\
Integration & 3.3e+09 & 0.00 & \includegraphics[width=0.33in, height=0.33in]{images/ball_BF_ext_integration.png}\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:table-sens-prior-analysis-ext}Bayes factor encompassing model and hypothesis posterior probabilities (PP) under different prior settings  ($n_{subj} = 847$).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{}rcccrcccrcc}
\toprule
\multicolumn{1}{c}{\textbf{ }} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, .5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 1)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 3)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 5)$}} & \multicolumn{2}{c}{\textbf{$\mathcal{N}(0, 10)$}} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11}
\textbf{Hypothesis} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP} & \textbf{BF} & \textbf{PP}\\
\midrule
\textbf{Null} & 8.9e+01 & 0.00 & 9.0e+04 & 0.00 & 2.4e+11 & 0.01 & 5.2e+14 & 0.03 & 1.4e+19 & 0.09\\
\textbf{Monotropy} & 1.1e+05 & 0.67 & 6.6e+07 & 0.90 & 2.5e+13 & 0.98 & 1.7e+16 & 0.97 & 1.3e+20 & 0.90\\
\textbf{Hierarchy} & 4.5e+04 & 0.28 & 6.5e+06 & 0.09 & 2.9e+11 & 0.01 & 6.8e+13 & 0.00 & 1.3e+17 & 0.00\\
\textbf{Independence} & 4.0e+03 & 0.02 & 2.8e+05 & 0.00 & 4.0e+09 & 0.00 & 5.8e+11 & 0.00 & 5.6e+14 & 0.00\\
\textbf{Integration} & 4.1e+03 & 0.03 & 3.5e+05 & 0.00 & 3.3e+09 & 0.00 & 3.3e+11 & 0.00 & 1.6e+14 & 0.00\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{r2\_ext}
\DocumentationTok{\#\#     Estimate  Est.Error       Q2.5     Q97.5}
\DocumentationTok{\#\# R2 0.1484309 0.02931432 0.09501877 0.2107168}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Argument 'nsamples' is deprecated. Please use argument 'ndraws' instead.
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{r2\_int}
\DocumentationTok{\#\#     Estimate  Est.Error      Q2.5     Q97.5}
\DocumentationTok{\#\# R2 0.2224078 0.02975503 0.1660707 0.2825445}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning: Argument 'nsamples' is deprecated. Please use argument 'ndraws' instead.
\end{verbatim}
